Code used to generate paper results : Database comparison and CT characteristics

### 2024-10-04 Paper_code-Database_Comparison.Rmd
Changes in size figure

```{r, eval = TRUE, echo = FALSE}
pdf(file = paste0("figs/CTdatabase_comparison.pdf"),
    paper = "a4r")
plot(CTdatabase_ours, gp = gp)
upset(upset_CTdatabase,
      text.scale = upset_text_size,
      mb.ratio = c(0.6, 0.4))
dev.off()
```

@@

```{r, eval = TRUE, echo = FALSE}
pdf(file = paste0("figs/Jamin_comparison.pdf"))
plot(core_ours, gp = gp)
upset(upset_Jamin,
      text.scale = upset_text_size)
dev.off()
```

@@

```{r, eval = TRUE, echo = FALSE}
pdf(file = paste0("figs/Wang_comparison.pdf"))
plot(Wang_ours, gp = gp)
upset(upset_Wang,
      text.scale = upset_text_size)
dev.off()
```

@@

```{r, eval = TRUE, echo = FALSE}
pdf(file = paste0("figs/Carter_comparison.pdf"))
plot(Carter_ours, gp = gp)
upset(upset_Carter,
      text.scale = upset_text_size)
dev.off()
```

@@

```{r, eval = TRUE, echo = FALSE}
pdf(file = paste0("figs/Bruggeman_comparison.pdf"))
plot(Bruggeman_ours, gp = gp)
upset(upset_Bruggeman,
      text.scale = upset_text_size)
dev.off()
```

@@

```{r, eval = TRUE, echo = FALSE}
pdf(file = paste0("figs/upset_all_lost.pdf"))
upset(upset_all,
      text.scale = upset_text_size)
dev.off()

pdf(file = paste0("figs/upset_all_databases.pdf"))
upset(upset_all_database,
      nsets = 6,
      nintersects = 50,
      text.scale = upset_text_size_all)
dev.off()
```

>>>>

```{r, eval = FALSE, echo = FALSE}
gp_no_label <- gp
gp_no_label[["SetText"]][["Set2"]]$fontsize <-  0
gp_no_label[["SetText"]][["Set1"]]$fontsize <- 0
gp_no_label[["FaceText"]][["11"]]$fontsize <- 40
gp_no_label[["FaceText"]][["10"]]$fontsize <- 40
gp_no_label[["FaceText"]][["01"]]$fontsize <- 40
pdf(file = paste0("figs/CTdatabase_comparison_venn.pdf"),
    height = 9, width = 5)
plot(CTdatabase_ours, gp = gp_no_label)
dev.off()

upset_text_size_save <- c(3, 2, 3, 2, 4, 4)
 #c(intersection size title, intersection size tick labels, set size title, 
 # set size tick labels, set names, numbers above bars)

pdf(file = paste0("figs/CTdatabase_comparison_upset.pdf"),
    height = 7, width = 8)
upset(upset_CTdatabase,
      text.scale = upset_text_size_save,
      mb.ratio = c(0.6, 0.4))
dev.off()
```

@@

```{r, eval = FALSE, echo = FALSE}
pdf(file = paste0("figs/Jamin_comparison.pdf"))
plot(core_ours, gp = gp)
upset(upset_Jamin,
      text.scale = upset_text_size)
dev.off()
```

@@

```{r, eval = FALSE, echo = FALSE}
pdf(file = paste0("figs/Wang_comparison.pdf"))
plot(Wang_ours, gp = gp)
upset(upset_Wang,
      text.scale = upset_text_size)
dev.off()
```

@@

```{r, eval = FALSE, echo = FALSE}
pdf(file = paste0("figs/Carter_comparison.pdf"))
plot(Carter_ours, gp = gp)
upset(upset_Carter,
      text.scale = upset_text_size)
dev.off()
```

@@

```{r, eval = FALSE, echo = FALSE}
pdf(file = paste0("figs/Bruggeman_comparison.pdf"))
plot(Bruggeman_ours, gp = gp)
upset(upset_Bruggeman,
      text.scale = upset_text_size)
dev.off()
```

@@

```{r, eval = FALSE, echo = FALSE}
pdf(file = paste0("figs/upset_all_lost.pdf"))
upset(upset_all,
      text.scale = upset_text_size)
dev.off()

upset_text_size_all_save <- c(3, 2, 3, 2, 4, 0)
 #c(intersection size title, intersection size tick labels, set size title, 
 # set size tick labels, set names, numbers above bars)

pdf(file = paste0("figs/upset_all_databases.pdf"),
    width = 15, height = 7)
upset(upset_all_database,
      nsets = 6,
      nintersects = 50,
      text.scale = upset_text_size_all_save,
      mb.ratio = c(0.55, 0.45))
dev.off()
```
